---
title: "Vignette"
author: "Chao Liu"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Package Description

`FARS` package imports and generates summary on fatal accidents based on data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.  The source data were from [Fatality Analysis Reporting System (FARS)](https://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS))

## Load Packages
```{r}
library(FARS)
```

## Load Data

Data files included in the package
```{r}
list.files(system.file("extdata", package = "FARS"))
```

## Package Functions

### Function `make_filename`

Argument should be one of 2013, 2014 or 2015
```{r}
make_filename(2013)
```

### Function `fars_read`
This function input csv file as data frame
```{r}
df_fars <- fars_read("accident_2013.csv.bz2")

head(df_fars, 3)
```

### Function `fars_read_years`
This function returns MONTH column of each year as a combined list. Input should be 2013, 2014, 2015, otherwise the function will generate an error message
This function uses `make_file_name` and `fars_read` as ancillary functions.

```{r}
fars_read_years(2013:2015)
```

### Function `fars_summarize_years`
This function returns the number of total fatal accident per month in 2013, 2014, 2015 respectively. It uses fars_read as ancillary functions.

```{r}
df_sum <- fars_summarize_years(2013:2015)

df_sum
```

### Function `fars_map_state`

```{r}
fars_map_state(state.num = 30, year = 2013)
```

